Report

### 2021-05-12 Rmd/report.Rmd
Add prime filter

Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$1 month) and language profile (similar exposure to a second language, $\pm$10%) that completed the same vocabulary checklist previously.

@@

@@

```{r gaze_time_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
gaze_time %>% 
	filter(valid_participant, valid_trial) %>% 
	group_by(participant, time_bin, trial_type, lp, age_group) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_wrap(age_group~participant~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	# geom_point(shape = 1, stroke = 1, size = 0.5) +
	geom_text(aes(x = 0, y = 1, label =
				  	paste0(str_remove_all(participant, pattern = "[a-zA-Z]"),
				  		   "/", age_group, "mo/", lp)),
			  size = 2, colour = "black", hjust = 0) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		axis.text = element_text(size = 7),
		legend.title = element_blank(),
		legend.position = "top",
		strip.background = element_blank(),
		strip.text.x = element_blank()
	) +
	ggsave(here("Figures", "gaze_time_participant.png"), height = 12, width = 12)
```

>>>>

Vocabulary sizes of participants whose families failed to complete the vocabulary checklists were imputed, by assigning them the most likely vocabulary size from a distribution of vocabulary sizes of children of similar age ($\pm$ 1 month) and language profile (similar exposure to a second language, $\pm$ 10%) that completed the same vocabulary checklist previously.

@@

### Target fixations: Oxford vs. Barcelona {.tabset .tabset-pills}

```{r gaze_time_location_21, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

gaze_time_vocab_d %>% 
	filter(age_group == "21 months") %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~location) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

```{r gaze_time_location_25, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

gaze_time_vocab_d %>% 
	filter(age_group == "25 months") %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~location) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

```{r gaze_time_location_30, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE}

gaze_time_vocab_d %>% 
	filter(age_group == "30 months") %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~location) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	stat_summary(fun.data = mean_se, geom = "pointrange", size = 0.25) +
	#geom_line() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	#geom_point(alpha = 0.5) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(legend.title = element_blank(),
		  legend.position = "top",
		  panel.grid = element_line(colour = "grey", linetype = "dotted"))

#### {-}

# Data analysis {.tabset .tab-pills}

## Model

$$
\log(\frac{p}{n - q}) &=& (\beta_{0} + \beta_{0p} + \beta_{0i}) + ... \\
(\beta_{1} + \beta_{1p} + \beta_{1i})\times Condition_{pi} + ... \\
(\beta_{2} + \beta_{2i}) \times Group_{pi} + ... \\
(\beta_{3} + \beta_{3i}) \times (Condition_{pi} \times Group_{pi}) + ... \\
(\beta_{4} + \beta_{4p}) \times Vocabulary_{p} + \varepsilon_{pi}
$$

@@

```{r gaze_time_participant, echo=FALSE, message=FALSE, warning=FALSE, paged.print=FALSE, fig.height=8}
gaze_time %>% 
	group_by(participant, time_bin, trial_type, lp, age_group) %>% 
	summarise(
		prop = mean(prop, na.rm = TRUE),
		n = n(),
		.groups = "drop"
	) %>% 
	ungroup() %>% 
	mutate(
		se = sqrt((prop*(1-prop))/(n+4)),
		lower = prop-se,
		upper = prop+se
	) %>% 
	drop_na() %>% 
	ggplot(aes(x = time_bin, y = prop, colour = trial_type, fill = trial_type)) +
	facet_wrap(age_group~participant~lp) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	geom_smooth() +
	#geom_ribbon(aes(ymin = lower, ymax = upper), width = 0) 
	# geom_point(shape = 1, stroke = 1, size = 0.5) +
	geom_text(aes(x = 0, y = 1, label =
				  	paste0(str_remove_all(participant, pattern = "[a-zA-Z]"),
				  		   "/", age_group, "mo/", lp)),
			  size = 2, colour = "black", hjust = 0) +
	labs(x = "Time bin (100 ms)", y = "Fixations", colour = "Condition", fill = "Condition") +
	scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
	scale_colour_brewer(palette = "Set1") +
	scale_fill_brewer(palette = "Set1") +
	theme_bilingual() +
	theme(
		axis.text = element_text(size = 7),
		legend.title = element_blank(),
		legend.position = "top",
		strip.background = element_blank(),
		strip.text.x = element_blank()
	) +
	ggsave(here("Figures", "gaze_time_participant.png"), height = 12, width = 12)
```
